ISYE 6740 HW 1

### 2024-08-29 homework1.tex
Small changes

Per the source I've linked below, the Mahalnobis distance is the relative distance of point $x_i$, from the center
of mass y (in our case, the centroid Mu_j). The transpose vector of $x_i$ - $Mu_j$ is multiplied by the
inverse of the covariance matrix multiplied by $x_i$ - $Mu_j$. This essentially introduces a normalization
component. Additionally, like our squared euclidean distance in the prior problem, we have the squared
Mahalanobis distance. The steps we take will be identical to those we took to solve for the
respective $Mu_j$ and $r_{ij}$ of the euclidean squared distance. However, now we simply have an additional
covariance term to be concerned with. I'll skip ahead to the parts that will look different.
\begin{equation}
\frac{\partial J}{\partial \boldsymbol{\mu}_j} = -2 \sum_{i=1}^{m} r_{ij} \Sigma (\mathbf{x}_i - \boldsymbol{\mu}_j)
\]

>>>>

Per the source I've linked below, the Mahalnobis distance is the relative distance of point $x_i$, from the center
of mass y (in our case, the centroid $Mu_j$). The transpose vector of $x_i$ - $Mu_j$ is multiplied by the
inverse of the covariance matrix multiplied by $x_i$ - $Mu_j$. This essentially introduces a normalization
component. Additionally, like our squared euclidean distance in the prior problem, we have the squared
Mahalanobis distance. The steps we take will be identical to those we took to solve for the
respective $Mu_j$ and $r_{ij}$ of the euclidean squared distance. However, now we simply have an additional
covariance term to be concerned with. I'll skip ahead to the parts that will look different.
\begin{equation}
\frac{\partial J}{\partial \boldsymbol{\mu}_j} = -2 \sum_{i=1}^{m} r_{ij} \Sigma (\mathbf{x}_i - \boldsymbol{\mu}_j)
\end{equation}
